dyngen: simulating developing single cells

### 2019-09-21 content.tex
update pdf

\mycomment{→ basically an ODE}
When simulating the developmental backbone, we go through the edges of the backbone state network defined in an earlier step (Section \ref{sec:backbone}), starting from the root state. It is assumed the root state has no modules active and has no expression of any molecules. To get to next state, we follow a transition starting from the root state, activate and deactivate the modules as indicated by the transition, and compute the average molecule abundance along the transition. To compute the average abundance, we perform small time steps $t = 0.001$ and let each reaction (Section \ref{sec:reactions}) occur $t$ times its propensity.

>>>>

\mycomment{this is basically an ODE, though we never reference ODEs anywhere. Maybe this is ok, this simplifies the section a bit?}
When simulating the developmental backbone, we go through the edges of the backbone state network defined in an earlier step (Section \ref{sec:backbone}), starting from the root state. It is assumed the root state has no modules active and has no expression of any molecules. To get to next state, we follow a transition starting from the root state, activate and deactivate the modules as indicated by the transition, and compute the average molecule abundance along the transition. To compute the average abundance, we perform small time steps $t = 0.001$ and let each reaction (Section \ref{sec:reactions}) occur $t$ times its propensity.

### 2019-09-21 manuscript.tex
update
update pdf

\documentclass[11pt,hidelinks,a4paper]{article}

@@

@@

% used for defining abbreviations, see nomenclature.tex
\usepackage{nomencl}

@@

% references packages
\usepackage[sorting=none]{biblatex}
\bibliography{library}
\usepackage{bibentry}
\nobibliography*

@@

% fix named refs for starred sections
\makeatletter
\def\ttl@useclass#1#2{%
	\@ifstar
	{\ttl@labeltrue\@dblarg{#1{#2}}}% {\ttl@labelfalse#1{#2}[]}%
	{\ttl@labeltrue\@dblarg{#1{#2}}}}
\makeatother

@@

% use Sonny chapter style
\usepackage[Sonny]{fncychap} %Sonny

% set font after chapter sonny style
\usepackage{fontspec}
\setmainfont [Path = fonts/,
UprightFont = *-300,
ItalicFont = *-300-Italic,
BoldFont = *-700,
BoldItalicFont = *-700-Italic
]{MuseoSans}

%% hyperlinks
% load hyperref after fncychap
\usepackage{hyperref}

\renewcommand{\appendixname}{}
\renewcommand{\baselinestretch}{1.25}

@@

\include{content}

>>>>

\documentclass[11pt,a4paper]{article}

% dyngen

@@

\usepackage[margin=2.5cm,a4paper]{geometry}

@@

@@

% references packages
\usepackage[sorting=none]{biblatex}
\bibliography{library}
\usepackage{bibentry}

@@

% authors and affiliations
\usepackage{authblk}

% command for adding comments
\newcommand{\mycomment}[1]{\noindent\fbox{\parbox{\textwidth}{\color{red}#1}}}

@@

\usepackage{fontspec}
\setmainfont [Path = fonts/,
UprightFont = *-300,
ItalicFont = *-300-Italic,
BoldFont = *-700,
BoldItalicFont = *-700-Italic
]{MuseoSans}

%% hyperlinks
\usepackage{hyperref}

\renewcommand{\baselinestretch}{1.25}

@@

\title{dyngen: simulating developing single cells}

\newcommand{\afdambi}{1}
\newcommand{\afappmat}{2}
\newcommand{\afcmgg}{3}
\newcommand{\afcrig}{4}

\author[\afdambi,\afappmat,\afcmgg,\afcrig]{Robrecht~Cannoodt}
\author[\afdambi,\afappmat]{Wouter~Saelens}
\author[\afdambi,\afappmat,*]{Yvan~Saeys}

\affil[\afdambi]{{\footnotesize Data Mining and Modelling for Biomedicine group, VIB Center for Inflammation Research, Ghent, Belgium}}
\affil[\afappmat]{{\footnotesize Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent, Belgium}}
\affil[\afcmgg]{{\footnotesize Center of Medical Genetics, Ghent University Hospital, Ghent, Belgium}}
\affil[\afcrig]{{\footnotesize Cancer Research Institute Ghent (CRIG), Ghent, Belgium}}
\affil[*]{{\footnotesize Corresponding author, \href{mailto:yvan.saeys@ugent.be}{yvan.saeys@ugent.be}}}
\date{}

\maketitle

\input{content}

\appendix

\printbibliography
